VCF file filtering by common garden site

### 2020-02-13 analysis/common-garden-allele-balancing/1_VCF_file_filtering_by_common_garden_site.Rmd
Allow John to repeat freezing site selection analysis

```{r}
colSums(!is.na(phenotypes_wide_2019))
i=7
for(i in 1:10){
site <- sites$Site[i]

site_2019 <- phenotypes_wide_2019 %>%
  pivot_longer(cols = BRKG_EM1:TMPL_TC_EOS, names_to = "SITE_PHE", values_to = "Measurement") %>%
  separate(col = SITE_PHE, into = c("SITE", "_", "PHE"), sep = c(4,5)) %>%
  filter(SITE == site & !is.na(Measurement)) %>%
  group_by(PLANT_ID) %>%
  summarise(count = n())

writeLines(site_2019$PLANT_ID, con = paste0(site, "_2019"))
}

for(i in 1:10){
site <- sites$Site[i]
site_2018 <- phenotypes_2018 %>%
  pivot_longer(cols = BRKG_DEAD_2018:TMPL_TC_EOS_2018, names_to = "SITE_PHE", values_to = "Measurement") %>%
  separate(col = SITE_PHE, into = c("SITE", "_", "PHE"), sep = c(4,5)) %>%
  filter(SITE == site & !is.na(Measurement)) %>%
  group_by(PLANT_ID) %>%
  summarise(count = n()) 
writeLines(site_2018$PLANT_ID, con = paste0(site, "_2018"))
}

>>>>

```{r}
colSums(!is.na(phenotypes_wide_2019))

libswitch <- metadata %>%
  dplyr::select(PLANT_ID, LIBRARY)
i=7
for(i in 1:10){
site <- sites$Site[i]

site_2019 <- phenotypes_wide_2019 %>%
  pivot_longer(cols = BRKG_EM1:TMPL_TC_EOS, names_to = "SITE_PHE", values_to = "Measurement") %>%
  separate(col = SITE_PHE, into = c("SITE", "_", "PHE"), sep = c(4,5)) %>%
  filter(SITE == site & !is.na(Measurement)) %>%
  group_by(PLANT_ID) %>%
  summarise(count = n()) %>%
  left_join(libswitch, by = "PLANT_ID")

writeLines(site_2019$LIBRARY, con = paste0("LIBRARY/", site, "_2019"))
}

for(i in 1:10){
site <- sites$Site[i]
site_2018 <- phenotypes_2018 %>%
  pivot_longer(cols = BRKG_DEAD_2018:TMPL_TC_EOS_2018, names_to = "SITE_PHE", values_to = "Measurement") %>%
  separate(col = SITE_PHE, into = c("SITE", "_", "PHE"), sep = c(4,5)) %>%
  filter(SITE == site & !is.na(Measurement)) %>%
  group_by(PLANT_ID) %>%
  summarise(count = n())  %>%
  left_join(libswitch, by = "PLANT_ID")
writeLines(site_2018$LIBRARY, con = paste0("LIBRARY/", site, "_2018"))
}
